### 2013-03-28 doc/sosp13/method.tex
started int sort paragraph; added a few citations

\vspace{0.5ex}
\noindent{\bf IntSort:} \TODO{Write me Brandon Holt!}

>>>>

\vspace{0.5ex}
\noindent{\bf IntSort:} This sorting benchmark is taken from the NAS
Parallel Benchmark Suite~\cite{Bailey91thenas,nas3.3} and is one on
which the CrayXMT's early predecessor once held the world speed
record~\cite{TeraRecord}. The class D benchmark ranks a billion
uniformly distributed random integers using either a bucket or a counting sort
algorithm: both versions are built into their reference code with the
choice left to the benchmarker, the difference being the number and iteration
counts of a series of tight loop computations.  Bucket sort uses less space
than counting sort but executes a greater number of loops.  We chose
Bucket sort for Grappa; the Cray XMT benchmark runs faster when using
counting sort,so our comparison is based on those performance numbers.
